---
title: "Alcohol vs Seat choice"
author: "Candice Fallon"
date: "Spring 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
 Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
 you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
  
This boxplot shows that the heavy drinkers are mostly in the back.  
  
  
## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
  
People that sit in the back drink three times as much alcohol as the people that sit in the front and the middle by a long shot.  
  
## Inferential Tests

# Inferential

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The p-value is so small that is unlikely that alcohol consumption in all three seats is the same.  
  
## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```
  
The TukeyHSD plot shows that the people in the back drink a lot more that the people in the front; it shows the people in the back drink more than the people in the middle. The middle-front shows no evidence of difference in the average alcohol consumption.  
  
## Conclusions
  
The evidence shows that the people that consume more alcohol tend to sit in the back of the class.  
  